Community Analysis

### 2022-07-14 R/08-community-analysis.Rmd
Add new decontam results, add dbrda results, add new discussion draft, update methods

@@

```{r passage-dbrda}
if(file.exists("Output/passage_rare_dist_bray.rds")) {
  passage_rare_dist_bray <- 
    readRDS("Output/passage_rare_dist_bray.rds")
} else {
passage_rare_dist_bray <- avgdist(passage5_df, dmethod="bray", sample=seq_range[1])
  passage_rare_dist_bray %>% 
    saveRDS("Output/passage_rare_dist_bray.rds")
}

passage_dist_df <-
  passage_rare_dist_bray %>% 
  as.matrix %>% 
  as_tibble(rownames = "sample")

passage_meta_dist <-
  aes_data %>% 
  select(sample, passage_treat, passage, treat, ch4) %>% 
  distinct %>% 
  inner_join(passage_dist_df, by = "sample")

passage_dbrda_ch4 <- dbrda(passage_rare_dist_bray ~ rank(ch4), 
                      data = passage_meta_dist, 
                      na.action = "na.omit",
                      add = TRUE)

passage_dbrda_ch4 %>% 
  permutest(permutations = 9999)

passage_percent_explained <- 100 * eigenvals(passage_dbrda_ch4) / sum(eigenvals(passage_dbrda_ch4))

passage_dbrda_scores <-
  scores(passage_dbrda_ch4, display = "sites") %>% 
  as_tibble(rownames = "sample")

passage_dbrda_data <-
  aes_data %>% 
  select(sample, passage, treat, ch4) %>% 
  distinct %>% 
  inner_join(passage_dbrda_scores, by = "sample")

passage_dbrda_data %>%   
  ggplot(aes(x = dbRDA1, y = MDS1, shape = passage, color = treat)) +
  geom_point() +
  stat_ellipse(show.legend = FALSE) +
  coord_fixed() +
  scale_shape_discrete(name = "Passage") +
  scale_color_manual(name = "Treatment",
                       labels = c('Neutral', 'Positive'),
                       values = c('gray40', 'darkorange2')) +
  theme_bw() +
  theme(
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

@@

@@

@@

@@

```{r setup-differential-abundance-data}

@@

## Corncob

@@

## ANCOM

@@

## Aldex2

@@

## Comparison

### All Significant

@@

### Consensus Taxa

@@

>>>>

passage2_df <-
  aes_data %>%  
  filter(passage == "G2") %>% 
  group_by(asv) %>% 
  mutate(total = sum(count)) %>% 
  filter(total != 0) %>% 
  ungroup() %>% 
  select(-total) %>% 
  select(sample, asv, count) %>%
  pivot_wider(names_from = "asv", values_from = "count", values_fill = 0) %>% 
  as.data.frame()

rownames(passage2_df) <- passage2_df$sample
passage2_df <- passage2_df[, -1]

@@

```{r passage2-dbrda}
if(file.exists("Output/passage2_rare_dist_bray.rds")) {
  passage2_rare_dist_bray <- 
    readRDS("Output/passage2_rare_dist_bray.rds")
} else {
passage2_rare_dist_bray <- avgdist(passage2_df, dmethod="bray", sample=seq_range[1])
  passage2_rare_dist_bray %>% 
    saveRDS("Output/passage2_rare_dist_bray.rds")
}

passage2_dist_df <-
  passage2_rare_dist_bray %>% 
  as.matrix %>% 
  as_tibble(rownames = "sample")

passage2_meta_dist <-
  aes_data %>% 
  select(sample, passage_treat, passage, treat, ch4) %>% 
  distinct %>% 
  inner_join(passage2_dist_df, by = "sample")

passage2_dbrda_ch4 <- dbrda(passage2_rare_dist_bray ~ rank(ch4), 
                      data = passage2_meta_dist, 
                      na.action = "na.omit",
                      add = TRUE)

passage2_dbrda_permtest <- 
passage2_dbrda_ch4 %>% 
  permutest(permutations = 9999)

passage2_dbrda_permtest <- 
passage2_dbrda_ch4 %>% 
  anova(permutations = 9999) %>% 
  tidy()

passage2_percent_explained <- 100 * eigenvals(passage2_dbrda_ch4) / sum(eigenvals(passage2_dbrda_ch4))

passage2_dbrda_scores <-
  scores(passage2_dbrda_ch4, display = "sites") %>% 
  as_tibble(rownames = "sample")

passage2_dbrda_data <-
  aes_data %>% 
  select(sample, passage, treat, ch4) %>% 
  distinct %>% 
  inner_join(passage2_dbrda_scores, by = "sample")

passage2_dbrda_data %>%   
  ggplot(aes(x = dbRDA1, y = MDS1, shape = passage, color = treat)) +
  geom_point() +
  stat_ellipse(show.legend = FALSE) +
  coord_fixed() +
  scale_shape_discrete(name = "Passage") +
  scale_color_manual(name = "Treatment",
                       labels = c('Neutral', 'Positive'),
                       values = c('gray40', 'darkorange2')) +
  theme_bw() +
  theme(
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

@@

```{r passage5-dbrda}
if(file.exists("Output/passage5_rare_dist_bray.rds")) {
  passage5_rare_dist_bray <- 
    readRDS("Output/passage5_rare_dist_bray.rds")
} else {
passage5_rare_dist_bray <- avgdist(passage5_df, dmethod="bray", sample=seq_range[1])
  passage5_rare_dist_bray %>% 
    saveRDS("Output/passage5_rare_dist_bray.rds")
}

passage5_dist_df <-
  passage5_rare_dist_bray %>% 
  as.matrix %>% 
  as_tibble(rownames = "sample")

passage5_meta_dist <-
  aes_data %>% 
  select(sample, passage_treat, passage, treat, ch4) %>% 
  distinct %>% 
  inner_join(passage5_dist_df, by = "sample")

passage5_dbrda_ch4 <- dbrda(passage5_rare_dist_bray ~ rank(ch4), 
                      data = passage5_meta_dist, 
                      na.action = "na.omit",
                      add = TRUE)

passage5_dbrda_permtest <-
passage5_dbrda_ch4 %>% 
  anova(permutations = 9999) %>% 
  tidy

passage5_percent_explained <- 100 * eigenvals(passage5_dbrda_ch4) / sum(eigenvals(passage5_dbrda_ch4))

passage5_dbrda_scores <-
  scores(passage5_dbrda_ch4, display = "sites") %>% 
  as_tibble(rownames = "sample")

passage5_dbrda_data <-
  aes_data %>% 
  select(sample, passage, treat, ch4) %>% 
  distinct %>% 
  inner_join(passage5_dbrda_scores, by = "sample")

passage5_dbrda_data %>%   
  ggplot(aes(x = dbRDA1, y = MDS1, shape = passage, color = treat)) +
  geom_point() +
  stat_ellipse(show.legend = FALSE) +
  coord_fixed() +
  scale_shape_discrete(name = "Passage") +
  scale_color_manual(name = "Treatment",
                       labels = c('Neutral', 'Positive'),
                       values = c('gray40', 'darkorange2')) +
  theme_bw() +
  theme(
    plot.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```{r}
save(passage2_dbrda_permtest, 
     passage5_dbrda_permtest, 
     passage5_percent_explained,
     file = "Output/dbrda.RData")
```

@@

### Family

@@

### Genus

```{r}
g5n <- 
  aes_data %>% 
  filter(passage_treat == "G5N") %>% 
  select(Genus) %>% 
  distinct() %$%
  Genus

g5p <- 
  aes_data %>% 
  filter(passage_treat == "G5P") %>% 
  select(Genus) %>% 
  distinct() %$%
  Genus

n_not_p_prevalence <-
  aes_data %>% 
  filter(passage_treat == "G5N") %>% 
  filter(Genus %in% n_not_p) %>% 
  select(sample, Genus, count) %>% 
  mutate(prevalence = as.numeric(count > 0)) %>% 
  select(-count) %>% 
  group_by(Genus) %>% 
  summarize(prevalence = sum(prevalence))

p_not_n_prevalence <-
  aes_data %>% 
  filter(passage_treat == "G5P") %>% 
  filter(Genus %in% p_not_n) %>% 
  select(sample, Genus, count) %>% 
  mutate(prevalence = as.numeric(count > 0)) %>% 
  select(-count) %>% 
  group_by(Genus) %>% 
  summarize(prevalence = sum(prevalence))

p_not_n_prevalence %>% 
  ggplot(aes(x = prevalence)) +
  geom_histogram() +
  scale_x_continuous(breaks = 1:12) +
  theme_classic() +
  labs(title = "Unique to Neutral")

p_not_n_over_6 <- p_not_n_prevalence %>%
  filter(prevalence > 6)

n_not_p_over_6 <- n_not_p_prevalence %>%
  filter(prevalence > 6)

### Species

```{r}
g5n <- 
  aes_data %>% 
  filter(passage_treat == "G5N") %>% 
  select(Species) %>% 
  distinct() %$%
  Species

g5p <- 
  aes_data %>% 
  filter(passage_treat == "G5P") %>% 
  select(Species) %>% 
  distinct() %$%
  Species

n_not_p_prevalence <-
  aes_data %>% 
  filter(passage_treat == "G5N") %>% 
  filter(Species %in% n_not_p) %>% 
  select(sample, Species, count) %>% 
  mutate(prevalence = as.numeric(count > 0)) %>% 
  select(-count) %>% 
  group_by(Species) %>% 
  summarize(prevalence = sum(prevalence))

p_not_n_prevalence <-
  aes_data %>% 
  filter(passage_treat == "G5P") %>% 
  filter(Species %in% p_not_n) %>% 
  select(sample, Species, count) %>% 
  mutate(prevalence = as.numeric(count > 0)) %>% 
  select(-count) %>% 
  group_by(Species) %>% 
  summarize(prevalence = sum(prevalence))

p_not_n_prevalence %>% 
  ggplot(aes(x = prevalence)) +
  geom_histogram() +
  scale_x_continuous(breaks = 1:12) +
  theme_classic() +
  labs(title = "Unique to Neutral")

p_not_n_over_6 <- p_not_n_prevalence %>%
  filter(prevalence > 3)

n_not_p_over_6 <- n_not_p_prevalence %>%
  filter(prevalence > 3)

@@

### Family

```{r setup-differential-abundance-data-family}

@@

#### Corncob

@@

#### ANCOM

@@

#### Aldex2

@@

#### Comparison

##### All Significant

@@

##### Consensus Taxa

@@

### Genus

```{r setup-differential-abundance-data-genus}

aes_Genus_G5 <-
  aes_G5 %>% 
  select(asv, sample, treat, count, Genus) %>%
  group_by(sample, Genus) %>% 
  mutate(total = sum(count)) %>% 
  ungroup() %>% 
  select(sample, treat, Genus, total) %>% 
  distinct()

prevalent_families <- 
  aes_Genus_G5 %>% 
  group_by(Genus, treat) %>% 
  summarize(prev = sum(total > 0), .groups = "drop") %>% 
  pivot_wider(names_from = "treat", values_from = "prev", values_fill = 0) %>% 
  filter(N/12 > 0.1 & P/12 > 0.1) %$%
  Genus

otu_table <- 
  aes_Genus_G5 %>% 
  filter(Genus %in% prevalent_families) %>% 
  select(sample, Genus, total) %>% 
  pivot_wider(names_from = sample, values_from = total, values_fill = 0) %>% 
  as.data.frame()

sample_data <- aes_Genus_G5 %>% 
  select(sample, treat) %>% 
  distinct() %>% 
  as.data.frame()

#### Corncob

dt_data <- plot(da_analysis, 
                # level = c("Genus"), 
                data_only = TRUE)

#### ANCOM

#### Aldex2

# x.all_effect_1 %>% 
#   # inner_join(taxa_table, by = "asv")
#   ggplot(aes(y = reorder(Genus, effect), x = effect)) +
#   geom_point()

# x.all_effect_1 %>% 
#   select(Genus, effect)

#### Comparison

##### All Significant

# ALDEX2
aldex_taxa <- x.all_effect_1$Genus

at_least_one_taxa <-
	aes_Genus_G5 %>%
	group_by(sample) %>%
	mutate(rel_abund = (total / sum(total)) * 100) %>%
	filter(Genus %in% ancom_taxa | Genus %in% aldex_taxa | Genus %in% corncob_taxa) %>%
	mutate(Genus = str_replace(Genus, "(.*)", "*\\1*"),
	       Genus = str_replace(Genus, "\\*(.*)_unclassified\\*",
				    "Unclassified *\\1*"))

at_least_one_iqm <- 
	at_least_one_taxa %>%
	group_by(treat, Genus) %>%
	summarize(median = median(rel_abund), 
		  first_quartile = quart(rel_abund)[1],
		  third_quartile = quart(rel_abund)[2], .groups = "drop")

sort_order <-
	at_least_one_taxa %>%
	group_by(Genus) %>%
	summarize(median = median(rel_abund)) %>%
	arrange(median)

at_least_one_taxa$Genus <- factor(at_least_one_taxa$Genus, levels = sort_order$Genus)

at_least_one_taxa %>%
	ggplot(aes(x = rel_abund, y = Genus, color = treat)) +
	geom_point(position=position_jitterdodge()) +
	geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, fill = treat), 
			data = at_least_one_iqm, 
			position = position_dodge(width = 0.75), 
			shape = 21, 
			color = "black") +
	theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Relative Abundance (%)", y = NULL) +
	scale_color_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2'))

##### Consensus Taxa

```{r}
aldex_effect <-
  x.all_effect_1 %>% 
  select(Genus, effect)

all_taxa <-
	aes_Genus_G5 %>%
	group_by(sample) %>%
	mutate(rel_abund = (total / sum(total)) * 100) %>%
  left_join(aldex_effect, by = "Genus") %>% 
	filter(Genus %in% ancom_taxa & Genus %in% aldex_taxa & Genus %in% corncob_taxa) %>% 
  ungroup()

da_fams <-
  all_taxa %>% 
  select(Genus) %>% 
  distinct() %$%
  Genus

all_taxa <-
  all_taxa %>%
	mutate(Genus = str_replace(Genus, "(.*)", "*\\1*"),
	       Genus = str_replace(Genus, "\\*(.*)_unclassified\\*",
				    "Unclassified *\\1*"))
all_taxa$Genus[all_taxa$Genus == "Unclassified *0319-6G20*"] <- "Uncultured Genus 0319-6G20"
all_taxa$Genus[all_taxa$Genus == "Unclassified *Chloroplast*"] <- "Chloroplast"
all_taxa$Genus[all_taxa$Genus == "Unclassified *Armatimonadales*"] <- "Unclassified Armatimonadales"
all_taxa$Genus[all_taxa$Genus == "Unclassified *Gammaproteobacteria*"] <- "Unclassified Gammaproteobacteria"
all_taxa$Genus[all_taxa$Genus == "Unclassified *Kapabacteriales*"] <- "Unclassified Kapabacteriales"

all_iqm <- 
	all_taxa %>%
	group_by(treat, Genus) %>%
	summarize(median = median(rel_abund), 
		  first_quartile = quart(rel_abund)[1],
		  third_quartile = quart(rel_abund)[2], .groups = "drop")

sort_order <-
	all_taxa %>%
  select(Genus, effect) %>% 
  distinct() %>% 
  arrange(effect)
	# group_by(Genus) %>%
	# summarize(median = median(rel_abund)) %>%
	# arrange(median)

all_taxa$Genus <- factor(all_taxa$Genus, levels = sort_order$Genus)
all_iqm$Genus <- factor(all_iqm$Genus, levels = sort_order$Genus)
all_taxa <-
  all_taxa %>% 
  mutate(direction = if_else(effect > 0, 0, 1))
all_iqm <-
all_taxa %>% 
  select(Genus, direction) %>% 
  distinct() %>% 
  full_join(all_iqm, by = "Genus")
(p <-
	all_taxa %>%
	ggplot(aes(x = rel_abund, y = Genus, color = treat)) +
	geom_point(position=position_jitterdodge()) +
	geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, fill = treat), 
			data = all_iqm, 
			position = position_dodge(width = 0.75), 
			shape = 21, 
			color = "black") +
	theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Relative Abundance (%)", y = NULL) +
	scale_color_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2')) +
    facet_grid(direction ~ ., scale = "free_y", space = "free")  + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank()
))

# aes_Genus_rclr_plot <-
#   aes_Genus_rclr %>% 
# 	filter(Genus %in% ancom_taxa & Genus %in% aldex_taxa & Genus %in% corncob_taxa) %>% 
#   pivot_longer(G2:G5, names_to = "passage", values_to = "rclr") %>% 
#   select(Genus, treat, rep, passage, rclr) %>% 
#   distinct() %>% 	
#   mutate(Genus = str_replace(Genus, "(.*)", "*\\1*"),
# 	       Genus = str_replace(Genus, "\\*(.*)_unclassified\\*",
# 				    "Unclassified *\\1*"))
# 
# aes_Genus_rclr_plot$Genus[aes_Genus_rclr_plot$Genus == "Unclassified *0319-6G20*"] <- "Uncultured Genus 0319-6G20"
# aes_Genus_rclr_plot$Genus[aes_Genus_rclr_plot$Genus == "Unclassified *Chloroplast*"] <- "Chloroplast"
# aes_Genus_rclr_plot$Genus <- factor(aes_Genus_rclr_plot$Genus, levels = sort_order$Genus)
# ggplot(aes_Genus_rclr_plot, aes(x = rclr, y = Genus, color = treat)) +
#   facet_grid( ~ passage) +
#   geom_point(position = position_jitterdodge())

p_effect <-
	all_taxa %>%
	ggplot(aes(x = effect, y = Genus)) +
	geom_point() +

### Species

```{r setup-differential-abundance-data-species}

aes_Species_G5 <-
  aes_G5 %>% 
  select(asv, sample, treat, count, Species) %>%
  group_by(sample, Species) %>% 
  mutate(total = sum(count)) %>% 
  ungroup() %>% 
  select(sample, treat, Species, total) %>% 
  distinct()

prevalent_families <- 
  aes_Species_G5 %>% 
  group_by(Species, treat) %>% 
  summarize(prev = sum(total > 0), .groups = "drop") %>% 
  pivot_wider(names_from = "treat", values_from = "prev", values_fill = 0) %>% 
  filter(N/12 > 0.1 & P/12 > 0.1) %$%
  Species

otu_table <- 
  aes_Species_G5 %>% 
  filter(Species %in% prevalent_families) %>% 
  select(sample, Species, total) %>% 
  pivot_wider(names_from = sample, values_from = total, values_fill = 0) %>% 
  as.data.frame()

sample_data <- aes_Species_G5 %>% 
  select(sample, treat) %>% 
  distinct() %>% 
  as.data.frame()

#### Corncob

dt_data <- plot(da_analysis, 
                # level = c("Species"), 
                data_only = TRUE)

#### ANCOM

#### Aldex2

x.all_effect_1 <-
  x.all %>% 
  filter(abs(effect) > 1) %>% 
  as_tibble(rownames = "Species")

# x.all_effect_1 %>% 
#   # inner_join(taxa_table, by = "asv")
#   ggplot(aes(y = reorder(Species, effect), x = effect)) +
#   geom_point()

# x.all_effect_1 %>% 
#   select(Species, effect)

#### Comparison

##### All Significant

# ALDEX2
aldex_taxa <- x.all_effect_1$Species

at_least_one_taxa <-
	aes_Species_G5 %>%
	group_by(sample) %>%
	mutate(rel_abund = (total / sum(total)) * 100) %>%
	filter(Species %in% ancom_taxa | Species %in% aldex_taxa | Species %in% corncob_taxa) %>%
	mutate(Species = str_replace(Species, "(.*)", "*\\1*"),
	       Species = str_replace(Species, "\\*(.*)_unclassified\\*",
				    "Unclassified *\\1*"))

at_least_one_iqm <- 
	at_least_one_taxa %>%
	group_by(treat, Species) %>%
	summarize(median = median(rel_abund), 
		  first_quartile = quart(rel_abund)[1],
		  third_quartile = quart(rel_abund)[2], .groups = "drop")

sort_order <-
	at_least_one_taxa %>%
	group_by(Species) %>%
	summarize(median = median(rel_abund)) %>%
	arrange(median)

at_least_one_taxa$Species <- factor(at_least_one_taxa$Species, levels = sort_order$Species)

at_least_one_taxa %>%
	ggplot(aes(x = rel_abund, y = Species, color = treat)) +
	geom_point(position=position_jitterdodge()) +
	geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, fill = treat), 
			data = at_least_one_iqm, 
			position = position_dodge(width = 0.75), 
			shape = 21, 
			color = "black") +
	theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Relative Abundance (%)", y = NULL) +
	scale_color_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2'))

##### Consensus Taxa

```{r}
aldex_effect <-
  x.all_effect_1 %>% 
  select(Species, effect)

all_taxa <-
	aes_Species_G5 %>%
	group_by(sample) %>%
	mutate(rel_abund = (total / sum(total)) * 100) %>%
  left_join(aldex_effect, by = "Species") %>% 
	filter(Species %in% ancom_taxa & Species %in% aldex_taxa & Species %in% corncob_taxa) %>% 
  ungroup()

da_fams <-
  all_taxa %>% 
  select(Species) %>% 
  distinct() %$%
  Species

all_taxa <-
  all_taxa %>%
	mutate(Species = str_replace(Species, "(.*)", "*\\1*"),
	       Species = str_replace(Species, "\\*(.*)_unclassified\\*",
				    "Unclassified *\\1*"))
all_taxa$Species[all_taxa$Species == "Unclassified *0319-6G20*"] <- "Uncultured Species 0319-6G20"
all_taxa$Species[all_taxa$Species == "Unclassified *Chloroplast*"] <- "Chloroplast"
all_taxa$Species[all_taxa$Species == "Unclassified *Armatimonadales*"] <- "Unclassified Armatimonadales"
all_taxa$Species[all_taxa$Species == "Unclassified *Gammaproteobacteria*"] <- "Unclassified Gammaproteobacteria"
all_taxa$Species[all_taxa$Species == "Unclassified *Kapabacteriales*"] <- "Unclassified Kapabacteriales"

all_iqm <- 
	all_taxa %>%
	group_by(treat, Species) %>%
	summarize(median = median(rel_abund), 
		  first_quartile = quart(rel_abund)[1],
		  third_quartile = quart(rel_abund)[2], .groups = "drop")

sort_order <-
	all_taxa %>%
  select(Species, effect) %>% 
  distinct() %>% 
  arrange(effect)
	# group_by(Species) %>%
	# summarize(median = median(rel_abund)) %>%
	# arrange(median)

all_taxa$Species <- factor(all_taxa$Species, levels = sort_order$Species)
all_iqm$Species <- factor(all_iqm$Species, levels = sort_order$Species)
all_taxa <-
  all_taxa %>% 
  mutate(direction = if_else(effect > 0, 0, 1))
all_iqm <-
all_taxa %>% 
  select(Species, direction) %>% 
  distinct() %>% 
  full_join(all_iqm, by = "Species")
(p <-
	all_taxa %>%
	ggplot(aes(x = rel_abund, y = Species, color = treat)) +
	geom_point(position=position_jitterdodge()) +
	geom_pointrange(aes(x = median, xmax = third_quartile, xmin = first_quartile, fill = treat), 
			data = all_iqm, 
			position = position_dodge(width = 0.75), 
			shape = 21, 
			color = "black") +
	theme_bw() +
	theme(axis.text.y = element_markdown()) +
	labs(x = "Relative Abundance (%)", y = NULL) +
	scale_color_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2')) +
	scale_fill_manual(name = "Treatment",
			   labels = c('Neutral', 'Positive'),
			   values = c('gray40', 'darkorange2')) +
    facet_grid(direction ~ ., scale = "free_y", space = "free")  + 
theme(
  strip.background = element_blank(),
  strip.text.y = element_blank()
))

# aes_Species_rclr_plot <-
#   aes_Species_rclr %>% 
# 	filter(Species %in% ancom_taxa & Species %in% aldex_taxa & Species %in% corncob_taxa) %>% 
#   pivot_longer(G2:G5, names_to = "passage", values_to = "rclr") %>% 
#   select(Species, treat, rep, passage, rclr) %>% 
#   distinct() %>% 	
#   mutate(Species = str_replace(Species, "(.*)", "*\\1*"),
# 	       Species = str_replace(Species, "\\*(.*)_unclassified\\*",
# 				    "Unclassified *\\1*"))
# 
# aes_Species_rclr_plot$Species[aes_Species_rclr_plot$Species == "Unclassified *0319-6G20*"] <- "Uncultured Species 0319-6G20"
# aes_Species_rclr_plot$Species[aes_Species_rclr_plot$Species == "Unclassified *Chloroplast*"] <- "Chloroplast"
# aes_Species_rclr_plot$Species <- factor(aes_Species_rclr_plot$Species, levels = sort_order$Species)
# ggplot(aes_Species_rclr_plot, aes(x = rclr, y = Species, color = treat)) +
#   facet_grid( ~ passage) +
#   geom_point(position = position_jitterdodge())

p_effect <-
	all_taxa %>%
	ggplot(aes(x = effect, y = Species)) +
	geom_point() +
